### 2017-05-16 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
adding comments to reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: Shall we reference your work about verifying multithread ANSI-C programs? Yes, please. Also reference our journal paper about esbmc-gpu.}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you? Can you cite our TACAS 2014 paper? I suggest you to read that paper which briefly explains our memory model. Then you can properly reply to the reviewer and cite that paper.}\textcolor{green}{Eddie: Maybe he is talking about shared, register, global and local... We need to show that our memory model correctly represent such types...}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:}\textcolor{green}{Eddie: We have to comment on kernels, blocks and threads, in order to clarify that, showing that it it feasible ...}}
\end{quote}

>>>>

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Erickson: Could you implement this comment, please?} Lucas: Shall we reference your work about verifying multithread ANSI-C programs? Yes, please. Also reference our journal paper about esbmc-gpu.}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Erickson: Could you implement this comment, please?} Lucas: Can you cite our TACAS 2014 paper? I suggest you to read that paper which briefly explains our memory model. Then you can properly reply to the reviewer and cite that paper.\textcolor{green}{Eddie: Maybe he is talking about shared, register, global and local... We need to show that our memory model correctly represent such types...}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:}\textcolor{red}{Erickson: Could you implement this comment, please?} \textcolor{green}{Eddie: We have to comment on kernels, blocks and threads, in order to clarify that, showing that it it feasible ...}}
\end{quote}
